Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-03-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex

A free standing steel frame wall with a 12.7~mm thick, 2.44~m high by 1.22~m wide, calcium silicate board face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux. Marinite Type I is the commercial name of the non-combustible board used in these experiments.  It is normally used as a fire-resistant thermal insulation that also has structural strength. 90~\% of the board is composed of calcium silicate and calcium meta-silicate.  The remaining 10~\% of the board is composed of a combination of organic fibers, fiber glass filament and crystalline silica (quartz) ref BNZ MSDS.  Material properties that impact heat transfer were selected from the manufacturer's literature and are presented in the table below ref BNZ Marinite I.   
\begin{table}
	\centering
\begin{tabular}{|c|c|c|c|c|}
	\hline Density & \multicolumn{2}{c|}{Thermal Conductivity} & \multicolumn{2}{c|}{Specific Heat}   \\ 
    \hline (kg/m$^3$) & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
	\hline 737  & 24 & 0.13 & 93 & 0.28 \\ 
	\hline  & 205 & 0.12  & 205 & 0.30 \\ 
	\hline  & 316 & 0.11 & 316 & 0.32 \\ 
	\hline  & 425 & 0.12 & 425 & 0.34 \\ 
	\hline  & 538 & 0.12 &  &  \\ 
	\hline 
\end{tabular} 
\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ Marinite I.}
\label{tab:Marinite_Thermal_Properties}
\end{table}

@@

The gypsum wallboard used in all of these experiments was purchased at one time from one vendor in an effort to have the most similar panels for used between the experiments.  The physical features of the gypsum wallboard panels are given in the table below.   After receipt of the gypsum wallboard panels, the panels were laid out on the floor or the NIST Large Fire Research Laboratory, finished paper side up and painted with a roller.  The first coat was a latex primer.  Once the primer dried a top coat of white latex paint was applied.  After the panels dried paint thickness measurements were made with a ultra sonic XXXX.  Some of the panels were then cut-up into samples think about this perhaps this goes into the FP Comp

>>>>

A free standing steel frame wall with a 12.7~mm thick, 2.44~m high by 1.22~m wide, calcium silicate board face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux. Marinite Type I is the commercial name of the non-combustible board used in these experiments.  It is normally used as a fire-resistant thermal insulation that also has structural strength. 90~\% of the board is composed of calcium silicate and calcium meta-silicate.  The remaining 10~\% of the board is composed of a combination of organic fibers, fiber glass filament and crystalline silica (quartz) ref BNZ MSDS.  Material properties that impact heat transfer were selected from the manufacturer's literature and are presented in the table below ref BNZ Marinite I.

\begin{table}
	\centering
\begin{tabular}{|c|c|c|c|c|}
	\hline Density & \multicolumn{2}{c|}{Thermal Conductivity} & \multicolumn{2}{c|}{Specific Heat}   \\ 
    \hline (kg/m$^3$) & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
	\hline 737  & 24 & 0.13 & 93 & 0.28 \\ 
	\hline  & 205 & 0.12  & 205 & 0.30 \\ 
	\hline  & 316 & 0.11 & 316 & 0.32 \\ 
	\hline  & 425 & 0.12 & 425 & 0.34 \\ 
	\hline  & 538 & 0.12 &  &  \\ 
	\hline 
\end{tabular} 
\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ Marinite I.}
\label{tab:Marinite_Thermal_Properties}
\end{table}

@@

The gypsum wallboard used in these experiments is referred to as "regular" as opposed to a gypsum wallboard `Type C' or `Type X' which are used in fire rated assemblies.   The gypsum wallboard used in these experiments was purchased from same manufacturer in an effort to have the most similar panels for use between the experiments.  The physical features of the gypsum wallboard panels are given in the table below.

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline Density (kg/m$^3&)  &Thermal Conductivity   & Specific Heat  &  &  \\ 
		\hline   & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
		\hline 807  & 24 	& 0.14 	&  		& 1.09 \\ 
		\hline  	& 100 	& 0.15  &  		&  \\ 
		\hline  	&  &  &  &  \\ 
		\hline 790 	& 20 	& 0.18	& 20 	& 0.90 \\ 
		\hline  	& 100 	& 0.15 	& 100 	& 0.90 \\ 
		\hline  	& 200 	& 0.13 	& 200 	& 0.80 \\ 
		\hline  	& 500 	& 0.15 	& 500	& 0.90 \\ 
		\hline 
		\end{tabular} 
		\caption[Thermal properties for 12.7~mm gypsum wallboard]{Thermal properties for 12.7~mm gypsum wallboard}
		\label{tab:Gypsum wallboard_Thermal_Properties}
		\end{table}

% first two lines of table based on measurements of GB at NIST.  Lower 4 lines from Gross 1985

After receipt of the gypsum wallboard panels, the panels were laid out on the floor of the NIST Large Fire Research Laboratory, finished paper side up and painted with a roller.  The first coat was a latex primer.  Once the primer dried a top coat of white latex paint was applied.  After the panels dried paint thickness measurements were made with a ultra sonic XXXX.  Some of the panels were then cut-up into samples think about this perhaps this goes into the FP Comp
